A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-22 6_validation.tex
new beading schemes comparison (reviewer 1.3, 2.6)

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
We construct the over- and underfill area by comparing the shapes covered by each extrusion move \revise{(\cref{segment_visualization_simple})}{} with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
%
%
We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in see \cref{over_underfill}.
The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.

>>>>

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
We construct the over- and underfill area by comparing the shapes covered by each extrusion move \revise{(\cref{segment_visualization_simple})}{} with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
%
%
We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in \revise{see }{}\cref{over_underfill}.
The inward distributed scheme has a calculated overfill of \revise{\SI{0.24}{\percent}}{\SI{0.30}{\percent}} and an underfill of \revise{\SI{0.17}{\percent}}{\SI{0.24}{\percent}}.
This is lower compared to the uniform scheme, which results in \revise{\SI{1.2}{\percent}}{\SI{1.63}{\percent}} overfill and \revise{\SI{1.7}{\percent}}{\SI{1.62}{\percent}} underfill in the data set.
\iffalse
names ['naive', 'Constant', 'Center', 'Distributed', 'InwardDistributed']
overfill [  1.63223926  22.21073295   0.37059604   0.45119725   0.30226112]
outer_underfill [ 0.04664107  0.03232884  0.04357603  0.03494708  0.03475748]
underfill [ 1.62009421  0.0712721   0.76886316  0.2440984   0.24461937]
\fi

### 2020-01-22 8_discussion.tex
new beading schemes comparison (reviewer 1.3, 2.6)

\subsection{Comparison of beading schemes}
We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
Note that most overfill areas occur near regions of alternating bead width. 
For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.

In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e. the variation is within a factor of $3.6$.}
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e. the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.
However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.
Furthermore, from \cref{smoothness} we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall.
Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes.

>>>>

\subsection{Comparison of beading schemes}
We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average \revise{approximately}{} \revise{\SI{1}{\percent}}{\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
Note that most overfill areas occur near regions of alternating bead width. 
\revise{}{While the scheme results in short tool paths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
See \cref{statisticsfig}.}
For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
\revise{}{See top right of \cref{TEST_Constant_accuracy}.}

In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e. the variation is within a factor of $3.6$.}
\revise{}{However, it does produce some narrow underfill regions.}
\revise{
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
}{
Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of tool path angles below \SI{45}{\degree}.
See \cref{statisticsfig}.
}

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e. \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e. the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

\revise{It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.}
{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline acuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
%{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
%While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
\revise{However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.}{} % _
Furthermore, \revise{from \cref{smoothness} }{}we find that compared to evenly distributed, the inward distributed scheme produces \revise{smoother toolpaths overall}{less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.
Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes\revise{}{, while incurring little to no extra print time}.
